### 2014-10-21 PrivacyProtection-2014-09-09.tex
refined introduction to 7ToP

Many researchers seem to only ``focus on the ways in which privacy can be infringed'' \cite{7ToP}.
Thus they invest a great amount of work in defining threats to prohibit instead of describing why privacy is so valuable to us.
This way around one could derive measures to ensure and secure its value \cite{7ToP}.
One particular scholar who does this in the context of digital monitoring is Charles Fried.
He questioned, why we are so sensitive to violations of privacy.
But he did not assert privacy as an intrinsic value by itself, he rather sated:

@@

Depending on the conversation partner, we change the degree of intimate information we share if it is a total stranger, colleague, close friend or lover.
With close friends or lovers we share information of great intimacy we do not share with anyone else.
Moreover, we trust those friends or lovers to not reveal information about us to others by respecting their privacy.
Trust needs the possibility of unknown failure.
If we would constantly monitor our partners, they cannot fail unnoticed nor can they willingly share that information with us.
Thus they could not trust us anymore. \cite{CFried:Privacy}

@@

* We follow Fried in defining privacy as the ability to control data about personal information.

* What is the relation to legal aspects?

* What should be personal information?

* Use Seven Privacy Types be Friedewald, Finn and Wrigtht.

@@

Seven Types of Privacy based on four types of privacy by Clarke.
Clarke's four types are outdated by contemporary technologies and no longer adequate.
In order to fix this Friedewald, Finn and Wright extend the former four to the now introduced seven types privacy as follows:

@@

\item \textbf{Privacy of the Person.}

This type is the right keep body functions and body characteristics private.

Examples include:
\begin{itemize}
\item Body Characteristics: weight, height, shoulder width, \ldots
\item Biometric Properties: Fingerprints, DNA Sequence, \ldots
\item Medical Conditions: Orthopedic conditions (e.g.~limping), Having a cold, \ldots
\end{itemize}

@@

This type is also concerned with the ``protection against disclosure of personal matters'' through behaviour, however Clarke's distinction between ``casual observation \om systematic recording and storage of information about those activities'' is lifted.

Examples include:
\begin{itemize}
\item regular visit at church, bakery, doctors
\item sexual habits
\item political activities
\end{itemize}

@@

It ``aims to avoid the interception of communications'' either electronic or face-to-face.

Examples include:
\begin{itemize}
\item Contents of letters and emails
\item Personal direct communication
\item Right to free discussion, i.e.~without third parties listening
\end{itemize}

@@

This type is concerned with ``making sure that individual's data is not automatically available to other individuals and organizations''.
This is Informational Privacy in an intuitive sense.

Examples include:
\begin{itemize}
\item Phone number
\item IP address
\item Public-administrative Data (Date of Birth, Melderegister)
\item Data held by organizations, like Banks or Insurance Companies
\item All data that is stored in online services (facebook)
\end{itemize}

@@

This type is the right ``not to share their thoughts or feelings or to have those thoughts or feeling (sic!) revealed''.
It is concerned with (automatic) emotion detection.
This type is the counterpart the Privacy of the Person like body and mind are counterparts of one another (dualism).

Examples include:
\begin{itemize}
\item Current feeling: Depression, tiredness, stressed, awake
\item Thoughts in general.
\end{itemize}

@@

This type is the right ``to move about in public or semi-public space without being identified, tracked or monitored''.
Additionally this type is concerned with the protection of one's home and private places (``right to solitude''.

Examples include:
\begin{itemize}
\item GPS position tracking
\item Location of home address
\end{itemize}

@@

This type is the right ``to associate with whomever [one] wishes, without being monitored''.
It is concerned with the protection against the automatic record of one's contacts.
It does not imply that one is monitored because of the associations.

Examples include:
\begin{itemize}
\item Friends
\item Joining of organizations (e.g.~political parties)
\end{itemize}
\end{enumerate}

>>>>

Many researchers seem to only ``focus on the ways in which privacy can be infringed'' \cite{7ToP}.
Thus they invest a great amount of work in defining threats to prohibit instead of describing why privacy is so valuable to us.
This way around one could derive measures to ensure and secure its value \cite{7ToP}.
One particular scholar who does this in the context of digital monitoring is Charles Fried.
He questioned, why we are intuitively sensitive to violations of privacy.
But he did not assert privacy as an intrinsic value by itself, he rather sated:

@@

Depending on the conversation partner, we change the degree of intimate information we share if it is a total stranger, colleague, close friend or lover.
With close friends or lovers we share information of great intimacy we do not share with anyone else.
Moreover, we trust those persons to not reveal information about us to others by respecting their privacy.
Trust needs the possibility of unknown failure.
If we would constantly monitor our partners, they cannot fail unnoticed nor can they willingly share that information with us.
Thus they could not trust us anymore. \cite{CFried:Privacy}

@@

%* We follow Fried in defining privacy as the ability to control data about personal information.
%
%* What is the relation to legal aspects?
%
%* What should be personal information?
%
%* Use Seven Privacy Types be Friedewald, Finn and Wrigtht.

@@

Although we use Fried's definition of privacy as one's control over information about oneself, we do not feel safe relying only on that to conduct a privacy protection analysis.
We need additional means to analyze in more detail which aspects of our lives need protection.
Friedewald, Finn and Wright \cite{7ToP} introduced a privacy taxonomy called \textit{Seven Types of Privacy} that can be of help.
The seven types of privacy are an extension to the four types of privacy by Roger Clarke \cite{RClarke:4ToP}:
\begin{itemize}
\item Privacy of the Person
\item Privacy of Personal Behaviour
\item Privacy of Personal Communication
\item Privacy of Personal Data
\end{itemize}
However, Friedewald et al. felt that Clarke's taxonomy are technologically outdated and no longer adequate.
In order to fix this they extend the former four to the now introduced seven types privacy as follows:

@@

\item 
\textbf{Privacy of the Person}

This privacy type is generally concerned with one could best understand as biometric privacy. 
Friedewald et al. paraphrase it as \emph{``\om the right to keep body functions and body characteristics \om private''}. 
This includes but is not limited to measures like weight, height or shoulder width;
biometric identifiers like fingerprints and DNA sequences;
or medical conditions such as limping or having a cold. \cite{7ToP}

@@

This privacy type is concerned with one's activities in public as well as in private spaces. 
It includes but is not limited to religious practices, political activities and sexual preferences or habits. \cite{7ToP}

@@

This privacy type is concerned with one's communication in a broad sense.
It includes written correspondence, but also conversations conducted either vis-a-vis or via electronic devices.
Friedewald et al. put it as the right to free discussion without unknown interception by third parties. \cite{7ToP}

@@

This privacy type is concerned with the secrecy of one's personal data, especially its automatic disclosure to other individuals and organizations.
It includes data such as paychecks, insurance information or records of public administration.
However, it also refers to pictures taken without consent and digital identifiers like IP addresses or social security numbers. \cite{7ToP}

@@

This privacy type is the counterpart to Privacy of the Person like body and mind are counterparts of one another.
Comparable to the Privacy of Data and Image, Friedewald et al. state that one's thoughts and feelings must not be automatically revealed to others.
This could simply happen by the disclosure of one's diary or by technologies which allow emotion detection through biometric means.
One's body temperature or iris reflexes might infer stress or excitation. \cite{7ToP}

@@

This privacy type is concerned with one's movements in public spaces and the inviolateness of one's private spaces.
Friedewald et al. qualify the first dimension as one's right to move without being identified, tracked or monitored.
The second dimension is qualified as one's general right to solitude, especially the right to the inviolability of the home. \cite{7ToP}

@@

This privacy type is also put as group privacy.
Friedewald et al. state that one must have the possibility with whomever without being recorded.
Associations like friends or organizations such as political parties must not automatically  be recorded because one associates with them, and vice versa.
